POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2024-01-29 existing-mechanisations/existing-mechanisations.tex
some more entries in mech table

  weak HOAS encoding in Coq, no exotic terms. Proof of subject reduction.

@@

  Reference                          & Proof assistant        & Linearity & Binders & Coinduction & Limitations \\\hline

@@

  \cite{Cervesato2007}               & CLF                    &           & HOAS + substructural opsem       &             &   no metatheory          \\

@@

@@

>>>>

  weak HOAS encoding in Coq, based on \emph{concretions}, no exotic terms. Proof of subject reduction.

@@

  Reference                          & Proof assistant        & Linearity & Binders & Coinduction & Notes/Limitations \\\hline

@@

    \cite{ChaudhuriCM15}                     & Abella                &           & HOAS + $\nabla$        & bisimulation up to             &              \\
  \cite{Cervesato2007}               & CLF                    &  substructural op.\ semantics         & HOAS       &             &   \textbf{no metatheory}          \\

@@

    \cite{CicconeP20}                 & Agda                   & context splitting, labelled types           & well typed DB        &             &             \\

@@

    \cite{AmbalLS21}                    & Coq                    &           & DB + nameless         &             &      higher order pi       \\
